Research Cases

### 2025-10-11 Code/R/Research/cases_research.Rmd
C++ implementation of 1d series reconstruction from tensor

# Two periodics case
## Short series
```{r}
# no rates
rates.true <- c(0, 0)
rates_case <- "_nr"
# small equal rated
# rates.true <- c(-0.01, -0.01)
# plot.name <- "_ser"
# large equal rates
# rates.true <- c(-0.02, -0.02)
# plot.name <- "_ler"
# different rated
# rates.true <- c(-0.01, -0.02)
# plot.name <- "_dr"

# no freqs
freqs.true <- c(0, 0)
freqs_case <- "_nf"
# different freqs
# freqs.true <- c(0.2, 0.22)
# freqs_case <- "_df"
# close different freqs
# freqs.true <- c(0.02, 0.0205)
# freqs_case <- "_cdf"

>>>>

# Two periodics case
## Short series
```{r}
# no rates
# rates.true <- c(0, 0)
# rates_case <- "_nr"
# small equal rated
# rates.true <- c(-0.01, -0.01)
# plot.name <- "_ser"
# large equal rates
# rates.true <- c(-0.02, -0.02)
# plot.name <- "_ler"
# different rated
rates.true <- c(-0.01, -0.02)
rates_case <- "_dr"

# no freqs
# freqs.true <- c(0, 0)
# freqs_case <- "_nf"
# different freqs
freqs.true <- c(0.2, 0.22)
freqs_case <- "_df"
# close different freqs
# freqs.true <- c(0.02, 0.0205)
# freqs_case <- "_cdf"
